\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-30 notes/2loopNLSM.tex
Starting blurb about nonlocal.

>>>>

We now turn to exploring the use of non-local numerators to skirt the
incompatibility.  We expect that promoting the numerators to
sufficiently complicated rational functions of the momenta will
eventually produce a color-dual representation.  At worst one could
imagine diagram ``numerator'' functions where all possible propagators
of all diagrams appear in each diagram ``numerator's'' denominator, at
which point required contributions could be arbitrarily rearranged
between diagrams.  However, given the success of non-local loop
numerators in other contexts \cite{Square, WeinzierlBCJLagrangian,
  Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl}, we hope that
only relatively tame additional denominators are required.

As a first attempt at such a tame non-local representation,
